GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-03-02 paper/main.tex
modify some words

    To address this problem, we propose a genetic-based training-free NAS 
    algorithm with hybrid training-free score function, which combines three 
    highly heterogeneous training-free score functions to evaluate an architecture. 
    In this method, the genetic algorithm plays a role to guide the searches 
    of NAS algorithm while the hybrid training-free score function plays the 
    role to evaluate a new candidate architecture during the convergencr process 
    of GA. More precisely, the first score function is noise immunity for 
    neural architecture search without search (NINASWOT), as an evaluation of 
    pattern recognition, second one is Maximum-Entropy Detection (MAE-DET), 
    as an evaluation of the entropy of an architecture and the third one is 
    condition number of neural tangent kernel (NTK), as an evaluation of 
    the speed of converge.

>>>>

    To address this problem, we propose a genetic-based training-free NAS 
    algorithm with hybrid training-free score function, which combines three 
    highly heterogeneous training-free score functions to evaluate an architecture. 
    In this method, the genetic algorithm plays a role to guide the searches 
    of NAS algorithm while the hybrid training-free score function plays the 
    role to evaluate a new candidate architecture during the convergencr process 
    of GA. More precisely, the first score function is noise immunity for 
    neural architecture search without search (NINASWOT), as an evaluation of 
    pattern recognition ability, second one is maximum-entropy detection (MAE-DET), 
    as an evaluation of the entropy of an architecture and the third one is 
    condition number of neural tangent kernel (NTK), as an evaluation of 
    the speed of converge.
